---
title: "20SP SYS 6014 Project Proposal"
author: "Jiasheng Li"
date: "04/08/20"
output:
  beamer_presentation:
    colortheme: dolphin
    fig_caption: yes
    fig_height: 3
    fig_width: 3.5
    fonttheme: structuresmallcapsserif
    slide_level: 3
    theme: AnnArbor
    toc: no
  ioslides_presentation: default
  slidy_presentation: default
institute: jl2sp
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load packages, echo=FALSE, include=FALSE}
library(here)
```


```{r make_beamer_slides, include=FALSE, eval= FALSE}
library(rmarkdown)
render("", beamer_presentation(
  toc = FALSE,
  slide_level = NULL,
  number_sections = FALSE,
  incremental = FALSE,
  fig_width = 10,
  fig_height = 7,
  fig_crop = TRUE,
  fig_caption = TRUE,
  dev = "pdf",
  df_print = "default",
  theme = "default",
  colortheme = "default",
  fonttheme = "default",
  highlight = "default",
  template = "default",
  keep_tex = FALSE,
  keep_md = FALSE,
  latex_engine = "pdflatex",
  citation_package = c("none", "natbib", "biblatex"),
  self_contained = TRUE,
  includes = NULL,
  md_extensions = NULL,
  pandoc_args = NULL
)
```

### Motivation
* Patterns exist in time series.
* Forecasting and prediction can be achieved by several approaches.
* Problem: researches emphasize model evaluation, but rarely discuss decison making upon predicted data.
* Aim of this project: decision analysis based on prediction achieved by Long-short term memory (LSTM).

### Predictivce Maintenance Decision analysis: Problem Formulation
* Predictive Maintenance:  
predict when an in-service machine will fail, so that maintenance can be planned in advance.    
* Prediction component:  
  Regression: Predict the Remaining Useful Life (RUL).  
  Classification: Predict if an asset will fail within certain time frame (e.g. days).    
* Optimization component:  
  Statistical decision model.  

### Data set
* Training set
* Test set
* Ground Truth


### Steps
* Step 1: Data preparation and feature engineering
* Step 2: Train and evaluate model
* Step 3: Decision analysis

### Statistical Decision Model
Action set: $$\mathbb A = \{A_{s} :stop Engine, A_{c}:continue\}$$
If the oepration state attribute can be treated as a random variable, then state space can be described as: $$\mathbb X = \{X_{n}:Operational, X_{f}:failure\}$$
The actual data distribution will be updated based on data set. 
The predicted time series will be generated by LSTM.

### Statistical Decision Model
Parameter Space: $$\Theta = \mathbb R \times [argmin\{attributes\},argmax\{attributes\})$$ for each of attributes of data set.  
Prior Belief: the mean of cycles for each engine id.

### Statistical Decision Model
Payoffs:
It can be described as: the expected payoff can be described as the economic based on the decsions made by the given potential risk information. For example: if the decision maker choose to continue operating the engine in a window, then there will be a loss.
$$\textbf{E}(A_{s}|X_{n}) < 0 , \textbf{E}(A_{s}|X_{f}) = 0, 
\textbf{E}(A_{c}|X_{n}) = 0,  
\textbf{E}(A_{c}|X_{f}) < 0$$
Objective: Minimise potential loss.

